---
title: "FLowering phenology analysis"
output: html_document
---


Libraries required
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(broom)
library(ggforce)
library(stringr)
library(lubridate)
library(metafor)
```

Read in data - this was stitched together in "cleaning data and initial plots.R"

```{r}
floweringdata <- read.csv("floweringdatafull.csv")
floweringdatawithdaydate <- read.csv("floweringdatafullwithfulldates.csv") #this is the flowering data that have date resolved to day rather than assigned the specimens that only had month data to the 15th day of the month - these specimens have been deleted from this data
```

Get year and julian date from start of spring (July) as separate columns


```{r}
floweringdata$Year <- as.numeric(format(as.Date(floweringdata$datelong, format="%Y-%m-%d"), "%Y")) #this creates a column with just the year
floweringdata$Truefloweringdate <- abs(yday(floweringdata$datelong)) #this creates a column with just the day of the year (from 1 to 366)

## now we want to make our year start in June - so for every day that is before june, we want to add it to 366 so that it tacks on at the END of the season!!!

#first create a column stating whether we need to add 366 days or zero days
floweringdata$add366ornot <- ifelse(floweringdata$Truefloweringdate < 152, 366, 0)

#then add them together!
floweringdata$Dayofflowering <- floweringdata$Truefloweringdate + floweringdata$add366ornot

```

Repeat this chunk with data that has removed the points that were only resolved to month and only has points that have complete date data


```{r}
floweringdatawithdaydate$Year <- as.numeric(format(as.Date(floweringdatawithdaydate$datelong, format="%Y-%m-%d"), "%Y")) #this creates a column with just the year

floweringdatawithdaydate$Truefloweringdate <- abs(yday(floweringdatawithdaydate$datelong)) #this creates a column with just the day of the year (from 1 to 366)

## now we want to make our year start in June - so for every day that is before june, we want to add it to 366 so that it tacks on at the END of the season!!!

#first create a column stating whether we need to add 366 days or zero days
floweringdatawithdaydate$add366ornot <- ifelse(floweringdatawithdaydate$Truefloweringdate < 152, 366, 0)

#then add them together!
floweringdatawithdaydate$Dayofflowering <- floweringdatawithdaydate$Truefloweringdate + floweringdatawithdaydate$add366ornot

```


Subset only data showing FULL flowering

```{r}
FULLflowering <- subset(floweringdata, Binary=="1")
FULLfloweringresolveddate <- subset(floweringdatawithdaydate, Binary =="1")
```

Run all lms on each species for their year vs flowering time 

```{r}
mylms <- FULLflowering %>%
  nest_by(Species) %>%
  mutate(fit=list(lm(Dayofflowering ~ Year, data = data))) %>%
  summarise(tidy(fit))

mylmsdateresolved <- FULLfloweringresolveddate %>%
  nest_by(Species) %>%
  mutate(fit=list(lm(Dayofflowering ~ Year, data = data))) %>%
  summarise(tidy(fit))

```

Running a p-value correction due to multiple hypothesis testing - and then saving this as a csv file
```{r}
mylmcoefs$Pcorrected <- p.adjust(mylmcoefs$p.value, "holm")

write.csv(mylmcoefs, "linearregressionfullfloweringresults.csv")
```


Now again for flowering inititaion

Subset only data showing FULL flowering

```{r}
STARTflowering <- subset(floweringdata, Binary=="2")
```

Run all lms on each species for their year vs flowering time 

```{r}
mylmsstart <- STARTflowering %>%
  group_by(Species) %>%
  do(fit=lm(Dayofflowering ~ Year,.))

mylmstartcoefs <- as.data.frame(tidy(mylmsstart, fit))
```

Running a p-value correction due to multiple hypothesis testing - and then saving this as a csv file
```{r}
mylmstartcoefs$Pcorrected <- p.adjust(mylmstartcoefs$p.value, "holm")

write.csv(mylmstartcoefs, "linearregressionstartoffloweringresults.csv")
```


And all again for flowering end

```{r}
ENDflowering <- subset(floweringdata, Binary=="3")
```

Run all lms on each species for their year vs flowering time 

```{r}
mylmsend <- ENDflowering %>%
  group_by(Species) %>%
  do(fit=lm(Dayofflowering ~ Year,.))

mylmendcoefs <- as.data.frame(tidy(mylmsend, fit))
```

Running a p-value correction due to multiple hypothesis testing - and then saving this as a csv file
```{r}
mylmendcoefs$Pcorrected <- p.adjust(mylmendcoefs$p.value, "holm")

write.csv(mylmendcoefs, "linearregressionendoffloweringresults.csv")
```


FIGURE PLOTTING 

1)Peak flowering plots (Figure 1)

Function for graphs with significant relationships for peak flowering


```{r}
#nativespecies
significantscatterplotsnative <- function(Speciesname = "", value,...){
  FULLflowering %>%
    filter(str_detect(!!FULLflowering$Species, value)) %>%
    ggplot(aes(x=Year, y=Dayofflowering)) +
    geom_point(colour="darkseagreen4", size=5, alpha = 0.5) +
    geom_smooth(method=lm, colour ="darkseagreen4", se=F, size=4) +
    ggtitle(Speciesname) +
    theme_classic() +
    theme(plot.title = element_text(size = 35, face = "italic", hjust = 0.5)) +
    theme(axis.text=element_blank(),
          axis.title=element_blank()) +
  coord_cartesian(xlim = c(1870, 2020), ylim = c(150, 517))
}

#nonnativespecies
significantscatterplotsnonnative <- function(Speciesname = "", value,...){
  FULLflowering %>%
    filter(str_detect(!!FULLflowering$Species, value)) %>%
    ggplot(aes(x=Year, y=Dayofflowering)) +
    geom_point(colour="lightsalmon2", size=5, alpha = 0.5) +
    geom_smooth(method=lm, colour ="lightsalmon2", se=F, size=4) +
    ggtitle(Speciesname) +
    theme_classic() +
    theme(plot.title = element_text(size = 35, face = "italic", hjust = 0.5)) +
    theme(axis.text=element_blank(),
          axis.title=element_blank()) +
  coord_cartesian(xlim = c(1870, 2020), ylim = c(150, 517))
}
```

Function for graphs without significant relationships for peak flowering 

```{r}
#native species
scatterplotsnative <- function(Speciesname = "", value,...){
  FULLflowering %>%
    filter(str_detect(!!FULLflowering$Species, value)) %>%
    ggplot(aes(x=Year, y=Dayofflowering)) +
    geom_point(colour="darkseagreen4", size=5, alpha = 0.5) +
    ggtitle(Speciesname) +
    theme_classic() +
    theme(plot.title = element_text(size = 35, face = "italic", hjust = 0.5)) +
    theme(axis.text=element_blank(),
          axis.title=element_blank()) +
  coord_cartesian(xlim = c(1870, 2020), ylim = c(150, 517))
}

#nonnative species
scatterplots <- function(Speciesname = "", value,...){
  FULLflowering %>%
    filter(str_detect(!!FULLflowering$Species, value)) %>%
    ggplot(aes(x=Year, y=Dayofflowering)) +
    geom_point(colour="lightsalmon2", size=5, alpha = 0.5) +
    ggtitle(Speciesname) +
    theme_classic() +
    theme(plot.title = element_text(size = 35, face = "italic", hjust = 0.5)) +
    theme(axis.text=element_blank(),
          axis.title=element_blank()) +
  coord_cartesian(xlim = c(1870, 2020), ylim = c(150, 517))
}
```


Run each graph for each species :) 

1. Graph all the species with significant relationships

```{r}
Callistemoncitrinus <- significantscatterplotsnative(value = "Callistemon citrinus", Speciesname = "Callistemon citrinus")

Notelaealongifolia <- significantscatterplotsnative(value = "Notelaea longifolia", Speciesname = "Notelaea longifolia \n f. longifolia")

Oleaeuropaea <- significantscatterplotsnonnative(value = "Olea africana", Speciesname = "Olea europaea \n subsp. cuspidata")

Leptospermumtrinervium <- significantscatterplotsnative(value = "Leptospermum trinervium", Speciesname = "Leptospermum trinervium")

Melaleucalinariifolia <- significantscatterplotsnative(value = "Melaleuca linariifolia", Speciesname = "Melaleuca linariifolia")

Ligustrumlucidum <- significantscatterplotsnonnative(value = "Ligustrum lucidum", Speciesname = "Ligustrum lucidum")

Clematisaristata <- significantscatterplotsnative(value = "Clematis aristata", Speciesname = "Clematis aristata")

Telopeaspeciosissima <- significantscatterplotsnative(value = "Telopea speciosissima", Speciesname = "Telopea speciosissima")

Acaciasaligna <- significantscatterplotsnonantive(value = "Acacia saligna", Speciesname = "Acacia saligna")

Kunzeacapitata <- significantscatterplotsnative(value = "Kunzea capitata", Speciesname = "Kunzea capitata")

Echinopogoncaespitosus <- significantscatterplotsnative(value = "Echinopogon caespitosus", Speciesname = "Echinopogon caespitosus")

Cotoneasterglaucophyllus <- significantscatterplotsnonnative(value = "Cotoneaster glaucophyllus", Speciesname = "Cotoneaster glaucophyllus")


```

2. Graph all the species with non-singificant relationships

```{r}
Acaciaparramattensis <- scatterplotsnative(value = "Acacia parramattensis", Speciesname = "Acacia parramattensis")

Leucopogonmicrophyllus <- scatterplotsnative(value = "Leucopogon microphyllus", Speciesname = "Leucopogon microphyllus")

Droserapeltata <- scatterplotsnative(value = "Drosera peltata", Speciesname = "Drosera peltata")

Tetragonia <- scatterplotsnative(value = "Tetragonia tetragonioides", Speciesname = "Tetragonia tetragonioides")

Cyathochaetadiandra <- scatterplotsnative(value = "Cyathochaeta diandra", Speciesname = "Cyathochaeta diandra")

Anisopogonavenaceus <- scatterplotsnative(value = "Anisopogon avenaceus", Speciesname = "Anisopogon avenaceus")

Callicomaserratifolia <- scatterplotsnative(value = "Callicoma serratifolia", Speciesname = "Callicoma serratifolia")

Glochidionferd <- scatterplotsnative(value = "Glochidion ferdinandi", Speciesname = "Glochidion ferdinandi")

Pultenaeastipularis <- scatterplotsnative(value = "Pultenaea stipularis", Speciesname = "Pultenaea stipularis")

Ceratopetalumgummiferum <- scatterplotsnative(value = "Ceratopetalum gummiferum", Speciesname = "Ceratopetalum gummiferum")

Entolasiamarginata <- scatterplotsnative(value = "Entolasia marginata", Speciesname = "Entolasia marginata")

Acaciabinervia <- scatterplotsnative(value = "Acacia binervia", Speciesname = "Acacia binervia")

Ageratinaadenophora <- scatterplotsnonnative(value = "Ageratina adenophora", Speciesname = "Ageratina adenophora")

Angophorahispida <- scatterplotsnative(value = "Angophora hispida", Speciesname = "Angophora hispida")

Callistemonsalignus <- scatterplotsnative(value = "Callistemon salignus", Speciesname = "Callistemon salignus")

Micrantheumericoides <- scatterplotsnative(value = "Micrantheum ericoides", Speciesname = "Micrantheum ericoides")

Syncarpiaglomulifera <- scatterplotsnative(value = "Syncarpia glomulifera", Speciesname = "Syncarpia glomulifera")

Lonicerajaponica <- scatterplotsnonnative(value = "Lonicera japonica", Speciesname = "Lonicera japonica")

Viminariajuncea <- scatterplotsnative(value = "Viminaria juncea", Speciesname = "Viminaria juncea")

Angophoracostata <- scatterplotsnative(value = "Angophora costata", Speciesname = "Angophora costata")


Elaeocarpusreticulatus <- scatterplotsnative(value = "Elaeocarpus reticulatus", Speciesname = "Elaeocarpus reticulatus")

Solanumnigrum <- scatterplotsnonnative(value = "Solanum nigrum", Speciesname = "Solanum nigrum")

Cinnamomumcamphora <- scatterplotsnonnative(value = "Cinnamomum camphora", Speciesname = "Cinnamomum camphora")

Persoonialevis <- scatterplotsnative(value = "Persoonia levis", Speciesname = "Persoonia levis")

Bossiaeascolopendria <- scatterplotsnative(value = "Bossiaea scolopendria", Speciesname = "Bossiaea scolopendria")
```

Stitch all the plots together to create Figure 1

```{r}
figure1 <- grid.arrange(Acaciasaligna, Ageratinaadenophora, Cinnamomumcamphora, Cotoneasterglaucophyllus, Ligustrumlucidum, Lonicerajaponica, Oleaeuropaea, Solanumnigrum, Acaciabinervia, Acaciaparramattensis, Angophoracostata, Angophorahispida, Anisopogonavenaceus, Bossiaeascolopendria, Callicomaserratifolia, Callistemoncitrinus, Callistemonsalignus, Ceratopetalumgummiferum, Clematisaristata, Cyathochaetadiandra, Droserapeltata, Echinopogoncaespitosus, Elaeocarpusreticulatus, Entolasiamarginata, Glochidionferd, Kunzeacapitata, Leptospermumtrinervium, Leucopogonmicrophyllus, Melaleucalinariifolia, Micrantheumericoides, Notelaealongifolia, Persoonialevis, Pultenaeastipularis, Syncarpiaglomulifera, Telopeaspeciosissima, Tetragonia, Viminariajuncea, ncol=4)

#save plot

ggsave("figure1.tiff",
       plot= figure1, 
       device = "tiff",
       width = 23,
       height = 44,
       dpi = 100)
```

Pulling out some numbers for results section - species specific results that show the biology of my analysis

1) Peak flowerng significant species
```{r}
#for clematis aristata
Clematislm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Clematis aristata")
print(Clematislm)
summary(Clematislm)

#y =mx+b formula to get days of advancement per decade
clematisdayin1960 = (-0.3156*1960) + 894.9744
clematisdayin1950 = (-0.3156*1950) + 894.9744
clematisdayin1960 - clematisdayin1950



#for Notelaea longifolia
Notealaealm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Notelaea longifolia")
print(Notealaealm)
summary(Notealaealm)

#y =mx+b formula to get days of advancement per decade
notelaeadayin1960 = (-1.775*1960) + 3800.362 
notelaeadayin1950 = (-1.775*1950) + 3800.362 
notelaeadayin1960 - notelaeadayin1950



#and for Acacia saligna
Acaciasalignalm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Acacia saligna")
print(Acaciasalignalm)
summary(Acaciasalignalm)

#y =mx+b formula to get days of advancement per decade
acaciasalignadayin1950 = (-0.2835*1950) + 824.3194
acaciasalignadayin1960 = (-0.2835*1960) + 824.3194
acaciasalignadayin1960 - acaciasalignadayin1950


#and for ligustrum lucidum
Ligustrumlucidumlm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Ligustrum lucidum")
print(Ligustrumlucidumlm)
summary(Ligustrumlucidumlm)

#y =mx+b formula to get days of advancement per decade
ligustrumlucidumdayin1950 = (-0.4296*1950) + 1216.7412
ligustrumlucidumdayin1960 = (-0.4296*1960) + 1216.7412
ligustrumlucidumdayin1960 - ligustrumlucidumdayin1950

#and for Callistemon citrinus (significantly delayed)

Callistemoncitrinuslm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Callistemon citrinus")
print(Callistemoncitrinuslm)
summary(Callistemoncitrinuslm)

#y =mx+b formula to get days of advancement per decade
callistemoncitrinusdayin1950 = (0.8653*1950) + -1409.5469
callistemoncitrinusdayin1960 = (0.8653*1960) + -1409.5469
callistemoncitrinusdayin1960 - callistemoncitrinusdayin1950


#and for Olea europea subsp. cuspidata
Oleaeuropaealm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Olea africana")
print(Oleaeuropaealm)
summary(Oleaeuropaealm)

#y =mx+b formula to get days of advancement per decade
oleaeuropeadayin1950 = (0.4551*1950) + -585.0978 
oleaeuropeadayin1960 = (0.4551*1960) + -585.0978 
oleaeuropeadayin1960 - oleaeuropeadayin1950



#and for Leptospermum trinervium (significantly delayed)
Leptospermumtrilm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Leptospermum trinervium")
print(Leptospermumtrilm)
summary(Leptospermumtrilm)

#y =mx+b formula to get days of advancement per decade
leptospermumdayin1950 = (0.2738*1950) + -251.2975 
leptospermumdayin1960 = (0.2738*1960) + -251.2975 
leptospermumdayin1960 - leptospermumdayin1950

```

2) Initiation of flowering

```{r}
#for notelea longifolia

Notelealongiolialm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Notelaea longifolia")
print(Notelealongiolialm)
summary(Notelealongiolialm)

#y =mx+b formula to get days of advancement per decade
notelaeadayin1950 = (-0.6059*1950) + 1420.2698
notelaeadayin1960 = (-0.6059*1960) + 1420.2698
notelaeadayin1960 - notelaeadayin1950



# for persoonia levis

Persoonialevislm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Persoonia levis")
print(Persoonialevislm)
summary(Persoonialevislm)

#y =mx+b formula to get days of advancement per decade
persooniadayin1950 = (-1.781*1950) + 3850.041
persooniadayin1960 = (-1.781*1960) + 3850.041
persooniadayin1960 - persooniadayin1950



#for callicoma serratifolia

Callicomalm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Callicoma serratifolia")
print(Callicomalm)
summary(Callicomalm)

#y =mx+b formula to get days of advancement per decade
callicomadayin1950 = (-0.2064*1950) + 684.0831
callicomadayin1960 = (-0.2064*1960) + 684.0831
callicomadayin1960 - callicomadayin1950


# for Angophora hispida (delayed)

Angophorahispidalm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Angophora hispida")
print(Angophorahispidalm)
summary(Angophorahispidalm)

#y =mx+b formula to get days of advancement per decade
angophorahispidadayin1950 = (0.1604*1950) + 0.01344
angophorahispidadayin1960 = (0.1604*1960) + 0.01344
angophorahispidadayin1960 - angophorahispidadayin1950

```

3) for species end flowering time

(there were none that remained significant after multiple hypothesis testing)


Now wnat to analyse the difference in shifts between native and non-native species

Read in the data that states each species origin
```{r}
nativeintrodata <- read.csv("nativeintro.csv")
```


First I need to add a column for species' counts into the data frames with regression results - this is important for creating the error/variance that will weight each species in the meta-analyses

```{r}
#first step is to create a dataframe of just the species counts

#for FULL flowering 
countdataFULL <- FULLflowering %>%
  group_by(Species) %>%
  summarise(count = n())

#for the INITIATION of flowering
countdataSTART <- STARTflowering %>%
  group_by(Species) %>%
  summarise(count = n())

#for the END of flowering
countdataEND <- ENDflowering %>%
  group_by(Species) %>%
  summarise(count = n())



#the second step is to create data frames that have the regression results and the count data 
#at this step I also added a column for variance that will be required in the meta-analyses
#and I also add the confidence intervals for species as these will be required in the forest plots

#for FULL flowering
FULLregressions <- left_join(mylmcoefs, countdataFULL, by = "Species") %>% #stitching data togeter
  mutate(variance = ((std.error^2)/count)) %>% #adding variance
  mutate(CI = 1.96*variance) %>% #adding confidence intervals for the variance
  mutate(CIofSE = 1.96*std.error) #adding confidence intervals for the standard error

#for the INITIATION of flowering
STARTregressions <- left_join(mylmstartcoefs, countdataSTART, by = "Species") %>%
  mutate(variance = ((std.error^2)/count)) %>%
  mutate(CI = 1.96*variance) %>%
  mutate(CIofSE = 1.96*std.error)

#for the END of flowering
ENDregressions <- left_join(mylmendcoefs, countdataEND, by = "Species") %>%
  mutate(variance = ((std.error^2)/count)) %>%
  mutate(CI = 1.96*variance) %>%
  mutate(CIofSE = 1.96*std.error)




#the third step is to remove the rows with the terms for intercept - I just want the model terms (Year) as this is the effect term

#for FULL flowering
FULLregressions <- FULLregressions[FULLregressions$term != "(Intercept)",]

#for the INITIATION of flowering
STARTregressions <- STARTregressions[STARTregressions$term != "(Intercept)",]

#for the END of flowering
ENDregressions <- ENDregressions[ENDregressions$term != "(Intercept)",]
```


Now wnat to analyse the difference in shifts between native and non-native species

Read in the data that states each species origin
```{r}
nativeintrodata <- read.csv("nativeintro.csv")
```

Attach this dataframe to the other three regression results data frame
```{r}
FULLregressions <- left_join(FULLregressions, nativeintrodata, by = "Species")
STARTregressions <- left_join(STARTregressions, nativeintrodata, by = "Species")
ENDregressions <- left_join(ENDregressions, nativeintrodata, by = "Species")
```


Run a meta-analytic model to determine the difference between native and introduced species

1) for peak flowering time
```{r}
nativeintropeaklm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~NativeIntro, 
                         data = FULLregressions)

print(nativeintropeaklm)
```

2) for flowering initiaton
```{r}
nativeintrostartlm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~NativeIntro, 
                         data = STARTregressions)

print(nativeintrostartlm)

##this came out as significant so I want to get the BIOLOGICAL difference between native and non-native species initiation of flowering time

Nativestarts <- filter(STARTregressions, NativeIntro=="Native")
mean(Nativestarts$estimate)
#=-0.7684541
Introstarts <- filter(STARTregressions, NativeIntro=="Intro")
mean(Introstarts$estimate)
#-1.407122


-1.407122/-0.7684541
```

3)
```{r}
nativeintroendlm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~NativeIntro, 
                         data = ENDregressions)

print(nativeintroendlm)
```

Make figure 2 to display this in our manuscript

```{r}
#I prefer violin plots

#for peak flowering
nativeintropeakplot <- ggplot(data=FULLregressions, aes(x=NativeIntro, y=estimate, fill =NativeIntro)) +
  geom_violin() +
  scale_fill_manual(values = c("lightsalmon2", "darkseagreen4")) +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(nativeintropeakplot)



ggsave("figure2.tiff",
       plot= nativeintropeakplot, 
       device = "tiff",
       width = 30,
       height = 12,
       dpi = 100)

```

Joining all dataframes together so that I can use this for a phylo-analysis

```{r}
allregressions <- left_join(FULLregressions, STARTregressions, ENDregressions, by="Species")
#save this as a CSV

write.csv(allregressions, "allregressions.csv")

```


Now analysing if there is a relationship between growth form and flowering time advancement

First read in and merge growth form data  
```{r}
growthformdata <- read.csv("growthform.csv")

FULLregressions <- left_join(FULLregressions, growthformdata, by = "Species")
FULLregressions <- FULLregressions[!is.na(FULLregressions$Growthform),]
STARTregressions <- left_join(STARTregressions, growthformdata, by = "Species")
STARTregressions <- STARTregressions[!is.na(STARTregressions$Growthform),]
ENDregressions <- left_join(ENDregressions, growthformdata, by = "Species")
ENDregressions <- ENDregressions[!is.na(ENDregressions$Growthform),]
```

1) for peak flowering time
```{r}
growthformpeaklm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~Growthform, 
                         data = FULLregressions)

print(growthformpeaklm)
```


Plotting differences between growth forms for flowering time
```{r}
#for peak flowering
growthformpeakplot <- ggplot(data=FULLregressions, aes(x=Growthform, y=estimate)) +
  geom_violin(fill = "lightsalmon2") +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(growthformpeakplot)



ggsave("figure3.tiff",
       plot= growthformpeakplot, 
       device = "tiff",
       width = 30,
       height = 10,
       dpi = 100)
```

