---
title: "FLowering phenology analysis"
output: html_document
---


Libraries required
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(broom)
library(ggforce)
library(stringr)
library(lubridate)
library(metafor)
```

Read in data - this was stitched together in "cleaning data and initial plots.R"

```{r}
floweringdata <- read.csv("floweringdatafull.csv")
```

Get year and julian date from start of spring (July) as separate columns


```{r}
floweringdata$Year <- as.numeric(format(as.Date(floweringdata$datelong, format="%Y-%m-%d"), "%Y")) #this creates a column with just the year
floweringdata$Truefloweringdate <- abs(yday(floweringdata$datelong)) #this creates a column with just the day of the year (from 1 to 366)

## now we want to make our year start in June - so for every day that is before june, we want to add it to 366 so that it tacks on at the END of the season!!!

#first create a column stating whether we need to add 366 days or zero days
floweringdata$add366ornot <- ifelse(floweringdata$Truefloweringdate < 152, 366, 0)

#then add them together!
floweringdata$Dayofflowering <- floweringdata$Truefloweringdate + floweringdata$add366ornot

```

Subset only data showing FULL flowering

```{r}
FULLflowering <- subset(floweringdata, Binary=="1")
```

Run all lms on each species for their year vs flowering time 

```{r}
mylms <- FULLflowering %>%
  group_by(Species) %>%
  do(fit=lm(Dayofflowering ~ Year,.))

mylmcoefs <- as.data.frame(tidy(mylms, fit))
```

Running a p-value correction due to multiple hypothesis testing - and then saving this as a csv file
```{r}
mylmcoefs$Pcorrected <- p.adjust(mylmcoefs$p.value, "holm")

write.csv(mylmcoefs, "linearregressionfullfloweringresults.csv")
```


Now again for flowering inititaion

Subset only data showing FULL flowering

```{r}
STARTflowering <- subset(floweringdata, Binary=="2")
```

Run all lms on each species for their year vs flowering time 

```{r}
mylmsstart <- STARTflowering %>%
  group_by(Species) %>%
  do(fit=lm(Dayofflowering ~ Year,.))

mylmstartcoefs <- as.data.frame(tidy(mylmsstart, fit))
```

Running a p-value correction due to multiple hypothesis testing - and then saving this as a csv file
```{r}
mylmstartcoefs$Pcorrected <- p.adjust(mylmstartcoefs$p.value, "holm")

write.csv(mylmstartcoefs, "linearregressionstartoffloweringresults.csv")
```


And all again for flowering end

```{r}
ENDflowering <- subset(floweringdata, Binary=="3")
```

Run all lms on each species for their year vs flowering time 

```{r}
mylmsend <- ENDflowering %>%
  group_by(Species) %>%
  do(fit=lm(Dayofflowering ~ Year,.))

mylmendcoefs <- as.data.frame(tidy(mylmsend, fit))
```

Running a p-value correction due to multiple hypothesis testing - and then saving this as a csv file
```{r}
mylmendcoefs$Pcorrected <- p.adjust(mylmendcoefs$p.value, "holm")

write.csv(mylmendcoefs, "linearregressionendoffloweringresults.csv")
```


FIGURE PLOTTING 

1)Peak flowering plots (Figure 1)

Function for graphs with significant relationships for peak flowering

```{r}
significantscatterplots <- function(Speciesname = "", value,...){
  FULLflowering %>%
    filter(str_detect(!!FULLflowering$Species, value)) %>%
    ggplot(aes(x=Year, y=Dayofflowering)) +
    geom_point(colour="lightsalmon2", size=5, alpha = 0.5) +
    geom_smooth(method=lm, colour ="darkseagreen4", se=F, size=4) +
    ggtitle(Speciesname) +
    theme_classic() +
    theme(plot.title = element_text(size = 35, face = "italic", hjust = 0.5)) +
    theme(axis.text=element_blank(),
          axis.title=element_blank()) +
  coord_cartesian(xlim = c(1870, 2020), ylim = c(150, 517))
}
```

Function for graphs without significant relationships for peak flowering 

```{r}
scatterplots <- function(Speciesname = "", value,...){
  FULLflowering %>%
    filter(str_detect(!!FULLflowering$Species, value)) %>%
    ggplot(aes(x=Year, y=Dayofflowering)) +
    geom_point(colour="lightsalmon2", size=5, alpha = 0.5) +
    ggtitle(Speciesname) +
    theme_classic() +
    theme(plot.title = element_text(size = 35, face = "italic", hjust = 0.5)) +
    theme(axis.text=element_blank(),
          axis.title=element_blank()) +
  coord_cartesian(xlim = c(1870, 2020), ylim = c(150, 517))
}
```


Run each graph for each species :) 

1. Graph all the species with significant relationships

```{r}
Callistemoncitrinus <- significantscatterplots(value = "Callistemon citrinus", Speciesname = "Callistemon citrinus")

Notelaealongifolia <- significantscatterplots(value = "Notelaea longifolia", Speciesname = "Notelaea longifolia \n f. longifolia")

Oleaeuropaea <- significantscatterplots(value = "Olea africana", Speciesname = "Olea europaea \n subsp. cuspidata")

Leptospermumtrinervium <- significantscatterplots(value = "Leptospermum trinervium", Speciesname = "Leptospermum trinervium")

Melaleucalinariifolia <- significantscatterplots(value = "Melaleuca linariifolia", Speciesname = "Melaleuca linariifolia")

Ligustrumlucidum <- significantscatterplots(value = "Ligustrum lucidum", Speciesname = "Ligustrum lucidum")

Clematisaristata <- significantscatterplots(value = "Clematis aristata", Speciesname = "Clematis aristata")

Telopeaspeciosissima <- significantscatterplots(value = "Telopea speciosissima", Speciesname = "Telopea speciosissima")

Acaciasaligna <- significantscatterplots(value = "Acacia saligna", Speciesname = "Acacia saligna")

Kunzeacapitata <- significantscatterplots(value = "Kunzea capitata", Speciesname = "Kunzea capitata")

Echinopogoncaespitosus <- significantscatterplots(value = "Echinopogon caespitosus", Speciesname = "Echinopogon caespitosus")

Cotoneasterglaucophyllus <- significantscatterplots(value = "Cotoneaster glaucophyllus", Speciesname = "Cotoneaster glaucophyllus")


```

2. Graph all the species with non-singificant relationships

```{r}
Acaciaparramattensis <- scatterplots(value = "Acacia parramattensis", Speciesname = "Acacia parramattensis")

Leucopogonmicrophyllus <- scatterplots(value = "Leucopogon microphyllus", Speciesname = "Leucopogon microphyllus")

Droserapeltata <- scatterplots(value = "Drosera peltata", Speciesname = "Drosera peltata")

Tetragonia <- scatterplots(value = "Tetragonia tetragonioides", Speciesname = "Tetragonia tetragonioides")

Cyathochaetadiandra <- scatterplots(value = "Cyathochaeta diandra", Speciesname = "Cyathochaeta diandra")

Anisopogonavenaceus <- scatterplots(value = "Anisopogon avenaceus", Speciesname = "Anisopogon avenaceus")

Callicomaserratifolia <- scatterplots(value = "Callicoma serratifolia", Speciesname = "Callicoma serratifolia")

Glochidionferd <- scatterplots(value = "Glochidion ferdinandi", Speciesname = "Glochidion ferdinandi")

Pultenaeastipularis <- scatterplots(value = "Pultenaea stipularis", Speciesname = "Pultenaea stipularis")

Ceratopetalumgummiferum <- scatterplots(value = "Ceratopetalum gummiferum", Speciesname = "Ceratopetalum gummiferum")

Entolasiamarginata <- scatterplots(value = "Entolasia marginata", Speciesname = "Entolasia marginata")

Acaciabinervia <- scatterplots(value = "Acacia binervia", Speciesname = "Acacia binervia")

Ageratinaadenophora <- scatterplots(value = "Ageratina adenophora", Speciesname = "Ageratina adenophora")

Angophorahispida <- scatterplots(value = "Angophora hispida", Speciesname = "Angophora hispida")

Callistemonsalignus <- scatterplots(value = "Callistemon salignus", Speciesname = "Callistemon salignus")

Micrantheumericoides <- scatterplots(value = "Micrantheum ericoides", Speciesname = "Micrantheum ericoides")

Syncarpiaglomulifera <- scatterplots(value = "Syncarpia glomulifera", Speciesname = "Syncarpia glomulifera")

Lonicerajaponica <- scatterplots(value = "Lonicera japonica", Speciesname = "Lonicera japonica")

Viminariajuncea <- scatterplots(value = "Viminaria juncea", Speciesname = "Viminaria juncea")

Angophoracostata <- scatterplots(value = "Angophora costata", Speciesname = "Angophora costata")


Elaeocarpusreticulatus <- scatterplots(value = "Elaeocarpus reticulatus", Speciesname = "Elaeocarpus reticulatus")

Solanumnigrum <- scatterplots(value = "Solanum nigrum", Speciesname = "Solanum nigrum")

Cinnamomumcamphora <- scatterplots(value = "Cinnamomum camphora", Speciesname = "Cinnamomum camphora")

Persoonialevis <- scatterplots(value = "Persoonia levis", Speciesname = "Persoonia levis")

Bossiaeascolopendria <- scatterplots(value = "Bossiaea scolopendria", Speciesname = "Bossiaea scolopendria")
```

Stitch all the plots together to create Figure 1

```{r}
figure1 <- grid.arrange(Acaciasaligna, Ageratinaadenophora, Cinnamomumcamphora, Cotoneasterglaucophyllus, Ligustrumlucidum, Lonicerajaponica, Oleaeuropaea, Solanumnigrum, Acaciabinervia, Acaciaparramattensis, Angophoracostata, Angophorahispida, Anisopogonavenaceus, Bossiaeascolopendria, Callicomaserratifolia, Callistemoncitrinus, Callistemonsalignus, Ceratopetalumgummiferum, Clematisaristata, Cyathochaetadiandra, Droserapeltata, Echinopogoncaespitosus, Elaeocarpusreticulatus, Entolasiamarginata, Glochidionferd, Kunzeacapitata, Leptospermumtrinervium, Leucopogonmicrophyllus, Melaleucalinariifolia, Micrantheumericoides, Notelaealongifolia, Persoonialevis, Pultenaeastipularis, Syncarpiaglomulifera, Telopeaspeciosissima, Tetragonia, Viminariajuncea, ncol=4)

#save plot

ggsave("figure1.tiff",
       plot= figure1, 
       device = "tiff",
       width = 23,
       height = 44,
       dpi = 100)
```

Pulling out some numbers for results section - species specific results that show the biology of my analysis

1) Peak flowerng significant species
```{r}
#for clematis aristata
Clematislm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Clematis aristata")
print(Clematislm)
summary(Clematislm)

#y =mx+b formula to get days of advancement per decade
clematisdayin1960 = (-0.3156*1960) + 894.9744
clematisdayin1950 = (-0.3156*1950) + 894.9744
clematisdayin1960 - clematisdayin1950



#for Notelaea longifolia
Notealaealm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Notelaea longifolia")
print(Notealaealm)
summary(Notealaealm)

#y =mx+b formula to get days of advancement per decade
notelaeadayin1960 = (-1.775*1960) + 3800.362 
notelaeadayin1950 = (-1.775*1950) + 3800.362 
notelaeadayin1960 - notelaeadayin1950



#and for Acacia saligna
Acaciasalignalm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Acacia saligna")
print(Acaciasalignalm)
summary(Acaciasalignalm)

#y =mx+b formula to get days of advancement per decade
acaciasalignadayin1950 = (-0.2835*1950) + 824.3194
acaciasalignadayin1960 = (-0.2835*1960) + 824.3194
acaciasalignadayin1960 - acaciasalignadayin1950


#and for ligustrum lucidum
Ligustrumlucidumlm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Ligustrum lucidum")
print(Ligustrumlucidumlm)
summary(Ligustrumlucidumlm)

#y =mx+b formula to get days of advancement per decade
ligustrumlucidumdayin1950 = (-0.4296*1950) + 1216.7412
ligustrumlucidumdayin1960 = (-0.4296*1960) + 1216.7412
ligustrumlucidumdayin1960 - ligustrumlucidumdayin1950

#and for Callistemon citrinus (significantly delayed)

Callistemoncitrinuslm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Callistemon citrinus")
print(Callistemoncitrinuslm)
summary(Callistemoncitrinuslm)

#y =mx+b formula to get days of advancement per decade
callistemoncitrinusdayin1950 = (0.8653*1950) + -1409.5469
callistemoncitrinusdayin1960 = (0.8653*1960) + -1409.5469
callistemoncitrinusdayin1960 - callistemoncitrinusdayin1950


#and for Olea europea subsp. cuspidata
Oleaeuropaealm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Olea africana")
print(Oleaeuropaealm)
summary(Oleaeuropaealm)

#y =mx+b formula to get days of advancement per decade
oleaeuropeadayin1950 = (0.4551*1950) + -585.0978 
oleaeuropeadayin1960 = (0.4551*1960) + -585.0978 
oleaeuropeadayin1960 - oleaeuropeadayin1950



#and for Leptospermum trinervium (significantly delayed)
Leptospermumtrilm <- lm(Dayofflowering ~ Year, data = FULLflowering, subset = Species=="Leptospermum trinervium")
print(Leptospermumtrilm)
summary(Leptospermumtrilm)

#y =mx+b formula to get days of advancement per decade
leptospermumdayin1950 = (0.2738*1950) + -251.2975 
leptospermumdayin1960 = (0.2738*1960) + -251.2975 
leptospermumdayin1960 - leptospermumdayin1950

```

2) Initiation of flowering

```{r}
#for notelea longifolia

Notelealongiolialm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Notelaea longifolia")
print(Notelealongiolialm)
summary(Notelealongiolialm)

#y =mx+b formula to get days of advancement per decade
notelaeadayin1950 = (-0.6059*1950) + 1420.2698
notelaeadayin1960 = (-0.6059*1960) + 1420.2698
notelaeadayin1960 - notelaeadayin1950



# for persoonia levis

Persoonialevislm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Persoonia levis")
print(Persoonialevislm)
summary(Persoonialevislm)

#y =mx+b formula to get days of advancement per decade
persooniadayin1950 = (-1.781*1950) + 3850.041
persooniadayin1960 = (-1.781*1960) + 3850.041
persooniadayin1960 - persooniadayin1950



#for callicoma serratifolia

Callicomalm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Callicoma serratifolia")
print(Callicomalm)
summary(Callicomalm)

#y =mx+b formula to get days of advancement per decade
callicomadayin1950 = (-0.2064*1950) + 684.0831
callicomadayin1960 = (-0.2064*1960) + 684.0831
callicomadayin1960 - callicomadayin1950


# for Angophora hispida (delayed)

Angophorahispidalm <- lm(Dayofflowering ~ Year, data = STARTflowering, subset = Species == "Angophora hispida")
print(Angophorahispidalm)
summary(Angophorahispidalm)

#y =mx+b formula to get days of advancement per decade
angophorahispidadayin1950 = (0.1604*1950) + 0.01344
angophorahispidadayin1960 = (0.1604*1960) + 0.01344
angophorahispidadayin1960 - angophorahispidadayin1950

```

3) for species end flowering time

(there were none that remained significant after multiple hypothesis testing)



Meta-analyses for each flowering stage shift (1: Peak, 2: Initation, 3: End)

First I need to add a column for species' counts into the data frames with regression results - this is important for creating the error/variance that will weight each species in the meta-analyses

```{r}
#first step is to create a dataframe of just the species counts

#for FULL flowering 
countdataFULL <- FULLflowering %>%
  group_by(Species) %>%
  summarise(count = n())

#for the INITIATION of flowering
countdataSTART <- STARTflowering %>%
  group_by(Species) %>%
  summarise(count = n())

#for the END of flowering
countdataEND <- ENDflowering %>%
  group_by(Species) %>%
  summarise(count = n())



#the second step is to create data frames that have the regression results and the count data 
#at this step I also added a column for variance that will be required in the meta-analyses
#and I also add the confidence intervals for species as these will be required in the forest plots

#for FULL flowering
FULLregressions <- left_join(mylmcoefs, countdataFULL, by = "Species") %>% #stitching data togeter
  mutate(variance = ((std.error^2)/count)) %>% #adding variance
  mutate(CI = 1.96*variance) %>% #adding confidence intervals for the variance
  mutate(CIofSE = 1.96*std.error) #adding confidence intervals for the standard error

#for the INITIATION of flowering
STARTregressions <- left_join(mylmstartcoefs, countdataSTART, by = "Species") %>%
  mutate(variance = ((std.error^2)/count)) %>%
  mutate(CI = 1.96*variance) %>%
  mutate(CIofSE = 1.96*std.error)

#for the END of flowering
ENDregressions <- left_join(mylmendcoefs, countdataEND, by = "Species") %>%
  mutate(variance = ((std.error^2)/count)) %>%
  mutate(CI = 1.96*variance) %>%
  mutate(CIofSE = 1.96*std.error)




#the third step is to remove the rows with the terms for intercept - I just want the model terms (Year) as this is the effect term

#for FULL flowering
FULLregressions <- FULLregressions[FULLregressions$term != "(Intercept)",]

#for the INITIATION of flowering
STARTregressions <- STARTregressions[STARTregressions$term != "(Intercept)",]

#for the END of flowering
ENDregressions <- ENDregressions[ENDregressions$term != "(Intercept)",]

# Done :) regression results are ready to be meta-analysed
```

Now I run the meta-analyses

1) Meta-analysis for peak flowering time across species
```{r}
FULLFloweringanalysis <- rma.uni(yi = estimate, vi = variance, data = FULLregressions)
print(FULLFloweringanalysis)

#RESULTS:
#estimate = 0.0040
#se = 0.0747

#create a dataframe with the ocerall result so that I can plot this in the forest plots
FULLoverall <- data.frame(Species = "Overall Effect", estimate = 0.0040, std.error = 0.0747)

FULLregressions <- bind_rows(FULLregressions, FULLoverall)

```

2) Meta-analysis for initiation of flowering time across species
```{r}
STARTFloweringanalysis <- rma.uni(yi = estimate, vi = variance, data = STARTregressions)
print(STARTFloweringanalysis)

#RESULTS:
#estimate = -0.4630
#se = 0.2487

#create a dataframe with the ocerall result so that I can plot this in the forest plots
STARToverall <- data.frame(Species = "Overall Effect", estimate = -0.4630, std.error = 0.2487)

STARTregressions <- bind_rows(STARTregressions, STARToverall)
```

3) Meta-analysis for the end of flowering time across species
```{r}
ENDFloweringanalysis <- rma.uni(yi = estimate, vi = variance, data = ENDregressions)
print(ENDFloweringanalysis)

#RESULTS:
#estimate = -0.0152
#se = 0.4860

#create a dataframe with the ocerall result so that I can plot this in the forest plots
ENDoverall <- data.frame(Species = "Overall Effect", estimate = -0.0152, std.error = 0.4860)

ENDregressions <- bind_rows(ENDregressions, ENDoverall)
```

Then I want to create Forest plots and stitch them together to make figure S1 for the supp info

First step is to create a vector of the species' names that I want to have the order of for the forest plots 
```{r}
SpeciesOrder <- c('Acacia saligna', 'Ageratina adenophora', 'Cinnamomum camphora', 'Cotoneaster glaucophyllus', 'Ligustrum lucidum', 'Lonicera japonica', 'Olea africana', 'Solanum nigrum', 'Acacia binervia', 'Acacia parramattensis', 'Angophora costata', 'Angophora hispida', 'Anisopogon avenaceus', 'Bossiaea scolopendria', 'Callicoma serratifolia', 'Callistemon citrinus', 'Callistemon salignus', 'Ceratopetalum gummiferum', 'Clematis aristata', 'Cyathochaeta diandra', 'Drosera peltata', 'Echinopogon caespitosus', 'Elaeocarpus reticulatus', 'Entolasia marginata', 'Glochidion ferdinandi', 'Kunzea capitata', 'Leptospermum trinervium', 'Leucophon microphyllus', 'Melaleuca linariifolia', 'Micrantheum ericoides', 'Notelaea longifolia', 'Persoonia levis', 'Pultenaea stipularis', 'Syncarpia glomulifera', 'Telopea speciosissima', 'Tetragonia tetragonioides', 'Viminaria juncea', 'Overall Effect')
```


Then create forest plots

1) Forest plot for full flowering

```{r}
Fullfloweringplot <- ggplot(data=FULLregressions, aes(y=factor(Species, level = SpeciesOrder), x=estimate)) +
  ylab("Species") +
  geom_errorbar(aes(xmin=estimate - std.error, xmax=estimate + std.error), colour ="darkseagreen4", size=1, width = 0.3) +
  geom_point(colour = 'darkseagreen4', size=5, shape=18, fill = 'darkseagreen4') +
  geom_errorbar(data=subset(FULLregressions, Species =="Overall Effect"), aes(xmin=estimate - std.error, xmax = estimate + std.error), colour = 'lightsalmon2', size = 1, width = 0.3) +
  geom_point(data=subset(FULLregressions, Species =="Overall Effect"), colour ="lightsalmon2", shape =15, size =4) +
  geom_vline(xintercept=0, size =0.5, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  scale_y_discrete(limits = unique(rev(SpeciesOrder))) +
  theme(axis.text.y = element_text(face='italic', size=22)) +
  theme(axis.text.x = element_text(size=28)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_text(size=40))
  
plot(Fullfloweringplot)  
```

2) Forest plot for initiation of flowering

```{r}
startfloweringplot <- ggplot(data=STARTregressions, aes(y=factor(Species, level = SpeciesOrder), x=estimate)) +
  ylab("Species") +
  geom_errorbar(aes(xmin=estimate - std.error, xmax=estimate + std.error), colour ="darkseagreen4", size=1, width = 0.3) +
  geom_point(colour = 'darkseagreen4', size=5, shape=18, fill = 'darkseagreen4') +
  geom_errorbar(data=subset(STARTregressions, Species =="Overall Effect"), aes(xmin=estimate - std.error, xmax = estimate + std.error), colour = 'lightsalmon2', size = 1, width = 0.3) +
  geom_point(data=subset(STARTregressions, Species =="Overall Effect"), colour ="lightsalmon2", shape =15, size =4) +
  geom_vline(xintercept=0, size =0.5, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  scale_y_discrete(limits = unique(rev(SpeciesOrder))) +
  theme(axis.text.y = element_blank()) +
  theme(axis.text.x = element_text(size=28)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank())
  
plot(startfloweringplot)
```

3)
```{r}
endfloweringplot <- ggplot(data=ENDregressions, aes(y=factor(Species, level = SpeciesOrder), x=estimate)) +
  ylab("Species") +
  geom_errorbar(aes(xmin=estimate - std.error, xmax=estimate + std.error), colour ="darkseagreen4", size=1, width = 0.3) +
  geom_point(colour = 'darkseagreen4', size=5, shape=18, fill = 'darkseagreen4') +
  geom_errorbar(data=subset(ENDregressions, Species =="Overall Effect"), aes(xmin=estimate - std.error, xmax = estimate + std.error), colour = 'lightsalmon2', size = 1, width = 0.3) +
  geom_point(data=subset(ENDregressions, Species =="Overall Effect"), colour ="lightsalmon2", shape =15, size =4) +
  geom_vline(xintercept=0, size =0.5, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  scale_y_discrete(limits = unique(rev(SpeciesOrder))) +
  theme(axis.text.y = element_blank()) +
  theme(axis.text.x = element_text(size=28)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank())
  
plot(endfloweringplot)
```

Then stitch all three plots along in a row together :)

```{r}
figureS1 <- grid.arrange(Fullfloweringplot, startfloweringplot, endfloweringplot, ncol=3, widths = c(1.50,1,1))

#save figure

ggsave("figureS1.tiff",
       plot= figureS1, 
       device = "tiff",
       width = 30,
       height = 12,
       dpi = 100)
```

Done :)

Now wnat to analyse the difference in shifts between native and non-native species

Read in the data that states each species origin
```{r}
nativeintrodata <- read.csv("nativeintro.csv")
```

Attach this dataframe to the other three regression results data frame
```{r}
FULLregressions <- left_join(FULLregressions, nativeintrodata, by = "Species")
STARTregressions <- left_join(STARTregressions, nativeintrodata, by = "Species")
ENDregressions <- left_join(ENDregressions, nativeintrodata, by = "Species")
```


Run a meta-analytic model to determine the difference between native and introduced species

1) for peak flowering time
```{r}
nativeintropeaklm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~NativeIntro, 
                         data = FULLregressions)

print(nativeintropeaklm)
```

2) for flowering initiaton
```{r}
nativeintrostartlm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~NativeIntro, 
                         data = STARTregressions)

print(nativeintrostartlm)

##this came out as significant so I want to get the BIOLOGICAL difference between native and non-native species initiation of flowering time

Nativestarts <- filter(STARTregressions, NativeIntro=="Native")
mean(Nativestarts$estimate)
#=-0.7684541
Introstarts <- filter(STARTregressions, NativeIntro=="Intro")
mean(Introstarts$estimate)
#-1.407122


-1.407122/-0.7684541
```

3)
```{r}
nativeintroendlm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~NativeIntro, 
                         data = ENDregressions)

print(nativeintroendlm)
```

Make figure 2 to display this in our manuscript

```{r}
#I prefer violin plots

#for peak flowering
nativeintropeakplot <- ggplot(data=FULLregressions, aes(x=NativeIntro, y=estimate, fill =NativeIntro)) +
  geom_violin() +
  scale_fill_manual(values = c("lightsalmon2", "darkseagreen4")) +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(nativeintropeakplot)


#for initiation of flowering
nativeintrostartplot <- ggplot(data=STARTregressions, aes(x=NativeIntro, y=estimate, fill =NativeIntro)) +
  geom_violin() +
  scale_fill_manual(values = c("lightsalmon2", "darkseagreen4")) +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), geom="pointrange", colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(nativeintrostartplot)


#for end of flowering
nativeintroendplot <- ggplot(data=ENDregressions, aes(x=NativeIntro, y=estimate, fill =NativeIntro)) +
  geom_violin() +
  scale_fill_manual(values = c("lightsalmon2", "darkseagreen4")) +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), geom="pointrange", colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(nativeintroendplot)

#stitch all three together

figure2 <- grid.arrange(nativeintropeakplot, nativeintrostartplot, nativeintroendplot, ncol=3)

ggsave("figure2.tiff",
       plot= figure2, 
       device = "tiff",
       width = 30,
       height = 12,
       dpi = 100)

```

Joining all dataframes together so that I can use this for a phylo-analysis

```{r}
allregressions <- left_join(FULLregressions, STARTregressions, ENDregressions, by="Species")
#save this as a CSV

write.csv(allregressions, "allregressions.csv")

```


Now analysing if there is a relationship between growth form and flowering time advancement

First read in and merge growth form data  
```{r}
growthformdata <- read.csv("growthform.csv")

FULLregressions <- left_join(FULLregressions, growthformdata, by = "Species")
FULLregressions <- FULLregressions[!is.na(FULLregressions$Growthform),]
STARTregressions <- left_join(STARTregressions, growthformdata, by = "Species")
STARTregressions <- STARTregressions[!is.na(STARTregressions$Growthform),]
ENDregressions <- left_join(ENDregressions, growthformdata, by = "Species")
ENDregressions <- ENDregressions[!is.na(ENDregressions$Growthform),]
```

1) for peak flowering time
```{r}
growthformpeaklm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~Growthform, 
                         data = FULLregressions)

print(growthformpeaklm)
```

2) for initation of flowering

```{r}
growthformstartlm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~Growthform, 
                         data = STARTregressions)

print(growthformstartlm)
```

3) for end of flowering

```{r}
growthformendlm <- rma(yi= estimate,
                         vi= variance,
                         mods= ~Growthform, 
                         data = ENDregressions)

print(growthformendlm)

#marginally significant overall relationship and significant difference between shrubs and herbs but not shrubs and trees
```

Plotting differences between growth forms for all three flowering stages

```{r}
#for peak flowering
growthformpeakplot <- ggplot(data=FULLregressions, aes(x=Growthform, y=estimate)) +
  geom_violin(fill = "lightsalmon2") +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(growthformpeakplot)


#for initiation of flowering
growthformstartplot <- ggplot(data=STARTregressions, aes(x=Growthform, y=estimate)) +
  geom_violin(fill = "lightsalmon2") +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(growthformstartplot)


#for end of flowering
growthformendplot <- ggplot(data=ENDregressions, aes(x=Growthform, y=estimate)) +
  geom_violin(fill = "lightsalmon2") +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult=1), colour="black") +
  theme_classic(base_size = 35) +
  theme(legend.position="none")

plot(growthformendplot)

#stitch all three together

figure3 <- grid.arrange(growthformpeakplot, growthformstartplot, growthformendplot, ncol=3)

ggsave("figure3.tiff",
       plot= figure3, 
       device = "tiff",
       width = 30,
       height = 10,
       dpi = 100)
```

