---
title: "flowering phenology phylogenetic analysis"
output: html_document
---

libraries required
```{r}
library(dplyr)
library(devtools)
library(V.PhyloMaker)
library(ggplot2)
library(nlme)
library(phytools)
library(gridExtra)
```

read in your data
- NB for a phylogenetic analysis we need to make sure we have three columns with these exact names - "species", "genus", "family" (beware of case)
- species will be a column of things that have the long species name, e.g. Banksia serrata
- genus will be a column of JUST the genus name, same e.g. Banksia
- family is the family of the species, same e.g. Proteacea

```{r}
phylodata <- read.csv("Speciesgenusfamily.csv")
```

Create a data frame with ONLY information about species, genus and family

```{r}
myspecieslist <- select(phylodata, "species", "genus", "family")
```

Getting our tree
we will run the following code which extracts a tree of JUST OUR species
- note that GBOTB.extended is the default tree, it is the one created by Smith and Borwn, 2018 with updated phylogenies
- output.sp.list = TRUE will mean that our tree will also spit out a list of what the analysis did to each species along the way, sometimes it bound the species to a tip in the tree, sometimes it prunes the species or sometimes it fails to bind the species to the backbone phylogeny - it is a good idea to check this list, because sometimes the "fail" is because there's a spelling error in the species/genus/family name
- output.tree = TRUE will allow the analysis to spit out a pretty little tree of our species
- scenarios is the choice we make about how to deal with species that are new and DON'T occur in the mega-tree. Scenario 3 ("S3"), I BELIEVE personally is the best way to deal with this - see Qian and Jin 2019 and Qian and Jin 2016 for a breakdown of the way each scenario works :)


```{r}
Phyloanalysis <- phylo.maker(myspecieslist, tree = GBOTB.extended, output.sp.list = TRUE, output.tree = TRUE, scenarios = "S3")

mytree <- Phyloanalysis$scenario.3 #creating just your tree (using scenario 3)
```

Plot that phylogeny to get a pretty tree diagram

```{r}
phyloplot <- plot.phylo(mytree, edge.width = 2, cex=1)

#And save that tree above
```


Now running a test for a phylogenetic signal

1. Make sure the branch labels (ie our species) match in the tree AND in our data frame

```{r}
# add a column with species' names with an underscore in them (because that's what V.phylomaker does to the species labels)
Species_ <- gsub(" ", "_", phylodata$species)
phylodata <- cbind(phylodata, Species_)

#make this column the row names 
rownames(phylodata) <- phylodata[,7]
```

2. Turn flowering shift estimates into a vector and add the species names to it

```{r}
#for full flowering
FULL <- as.vector(phylodata$fullestimate)
names(FULL) <- phylodata$Species_

#for initation of flowering
START <- as.vector(phylodata$startestimate)
names(START) <- phylodata$Species_

#for end of flowering
END <- as.vector(phylodata$endestimate)
names(END) <- phylodata$Species_
```

3. Run two analyses- one with lambda method and one with K method

```{r}
#for full flowering data
lambda <- phylosig(mytree, FULL, method="lambda", test=TRUE)
print(lambda)

K <- phylosig(mytree, FULL, method="K", test=TRUE)
print(K)

#for initation of flowering data
lambda <- phylosig(mytree, START, method="lambda", test=TRUE)
print(lambda)

K <- phylosig(mytree, START, method="K", test=TRUE)
print(K)

#for end of flowering data
lambda <- phylosig(mytree, END, method="lambda", test=TRUE)
print(lambda)

K <- phylosig(mytree, END, method="K", test=TRUE)
print(K)
```

Now, Making a graph of your tree with the shifts in flowering time to see if there's a pattern!

Steps:
1. Make a list of the species names in the ORDER as they appear in your tree (so that our graph will match up with the correct order)

```{r}
specieslist <- as.data.frame(Phyloanalysis$scenario.3$tip.label) %>%
  rename(species = `Phyloanalysis$scenario.3$tip.label`)

specieslist$species <- gsub("_", " ", specieslist$species)

```

2. Merge with flowering time data

```{r}
floweringtimedata <- left_join(specieslist, phylodata, by = "species")
```

3. create graph

```{r}
##lock in order of species
floweringtimedata$species <- factor(floweringtimedata$species, levels = floweringtimedata$species)

#plot full
FULLbyPHYLOplot <- ggplot(floweringtimedata, aes(x=fullestimate, y=species)) + geom_col(aes(fill = cut(fullestimate, c(-4,0,4)))) + 
  scale_fill_manual(name = "Full Estimate", values = c("(-4,0]" = "lightsalmon2", "(0,4]" = "darkseagreen")) +
  theme_classic() +
  theme(axis.text.y=element_text(size=10)) +
  theme(legend.position = "none")
plot(FULLbyPHYLOplot)

#plot start
STARTbyPHYLOplot <- ggplot(floweringtimedata, aes(x=startestimate, y=species)) + geom_col(aes(fill = cut(startestimate, c(-4,0,4)))) + 
  scale_fill_manual(name = "start Estimate", values = c("(-4,0]" = "lightsalmon2", "(0,4]" = "darkseagreen")) +
  theme_classic() +
  theme(axis.text.y=element_text(size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())
plot(STARTbyPHYLOplot)

#plot end
ENDbyPHYLOplot <- ggplot(floweringtimedata, aes(x=endestimate, y=species)) + geom_col(aes(fill = cut(endestimate, c(-4,0,4)))) + 
  scale_fill_manual(name = "end Estimate", values = c("(-4,0]" = "lightsalmon2", "(0,4]" = "darkseagreen")) +
  theme_classic() +
  theme(axis.text.y=element_text(size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())
plot(ENDbyPHYLOplot)

#stitchtogether

floweringshiftsinphylo <- grid.arrange(FULLbyPHYLOplot, STARTbyPHYLOplot, ENDbyPHYLOplot, ncol=3)

#save plot

ggsave(filename = "phyloplots.tiff", plot =  floweringshiftsinphylo, device = "tiff", dpi = 100, width= 25, height= 10, units = "in")
```
